Speculation in foreign exchange: noise or information

### 2015-05-10 Knitr/Paper.tex
Made a few changes.  Looks like a complete start is more apprppriate.

\documentclass[12pt, a4paper, oneside]{article} % Paper size, default font size and one-sided paper
%\usepackage[dcucite]{harvard}
\usepackage{tikz}
\usetikzlibrary{shapes, shadows, arrows}
\usepackage{rotating}
\usepackage{amsmath}
%\usepackage{setspace}
\usepackage{pdflscape}
\usepackage[flushleft]{threeparttable}
\usepackage{multirow}
\usepackage[comma, sort&compress]{natbib}% Use the natbib reference package - read up on this to edit the reference style; if you want text (e.g. Smith et al., 2012) for the in-text references (instead of numbers), remove 'numbers' 
\usepackage{graphicx}
\graphicspath{{./Figures/}} % Specifies the directory where pictures are stored
%\bibliographystyle{plainnat}
\usepackage{listings}
\bibliographystyle{agsm}
\usepackage[colorlinks = true, citecolor = blue, linkcolor = blue]{hyperref}
%\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue - change to black if annoying
\begin{document}
%\renewcommand[\harvardurl]{URL: \url}
\title{Speculation in foreign exchange: noise or information}
\author{Rob Hayward\footnote{University of Brighton Business School, Lewes Road, Brighton, BN2 4AT; Telephone 01273 642586.  rh49@brighton.ac.uk.  We are very grateful for the comments and suggestions made.  In particular, the EACES conference in Budapest between September 5th and 6th 2014, Andros Steinhoffer and.....}} 
\date{\today}
\maketitle
\begin{abstract}
An event study of extreme speculation is used to assess the Keynesian and Friedman views of speculation.  This is partly a test of the informational content of speculation.  Speculative extremes are ranked by weight of activity and intensity of sentiment.  In either case, the extreme says little about the future, suggesting that speculation is more than just noise and that there is some informational content that is being passed through to the price. A unique dataset of risk-reversal skew on option prices is used to measure the weight of speculative sentiment.  This is supplemented with regulatory data on the futures position of speculative traders.  
\end{abstract}

@@

This is a contrast between an idea of speculative activity as a nuisance that, at its most extreme, will likely to cause bubbles and reversal and will discourage fundamental long-term investors from participating in the market.  It is noise.   that does not emerge randomly, but feeds off itself as a feedback of sentiment  encourages  trends and serial correlation in asset prices returns.  The alternative view regards speculation as an key lubricant of financial market as it provides liquidity and facilitates price discovery.

The aim of this paper is to understand more about the nature of speculation in the foreign exchange market by assess the relationship between the intensity or the weight of speculation and the movement of prices.  If speculators are uninformed and their activity can be regarded as noise, their most extreme sentiment and the time when speculators have the greatest weight in market activity should be those when price reversals are most likely to take place.  An event study is used to assess the relationship between speculative extremes and foreign exchange returns.  A unique set of option prices are used to measure the intensity of speculative sentiment.  US regulatory positions measure the prominence of speculators in the market.

>>>>

\documentclass[12pt, a4paper, oneside]{article} % Paper size, default font size and one-sided paper
%\usepackage[dcucite]{harvard}
\usepackage{tikz}
\usetikzlibrary{shapes, shadows, arrows}
\usepackage{rotating}
\usepackage{amsmath}
%\usepackage{setspace}
\usepackage{pdflscape}
\usepackage[flushleft]{threeparttable}
\usepackage{multirow}
\usepackage[comma, sort&compress]{natbib}% Use the natbib reference package - read up on this to edit the reference style; if you want text (e.g. Smith et al., 2012) for the in-text references (instead of numbers), remove 'numbers' 
\usepackage{graphicx}
\graphicspath{{./Figures/}} % Specifies the directory where pictures are stored
%\bibliographystyle{plainnat}
\usepackage{listings}
\bibliographystyle{agsm}
\usepackage[colorlinks = true, citecolor = blue, linkcolor = blue]{hyperref}
%\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue - change to black if annoying
\begin{document}
%\renewcommand[\harvardurl]{URL: \url}
\title{Speculation in foreign exchange: noise or information}
\author{Rob Hayward\footnote{University of Brighton Business School, Lewes Road, Brighton, BN2 4AT; Telephone 01273 642586.  rh49@brighton.ac.uk.  We are very grateful for the comments and suggestions made.  In particular, the EACES conference in Budapest between September 5th and 6th 2014, Andros Steinhoffer and.....}} 
\date{\today}
\maketitle
\begin{abstract}
An event study of extremes is used to assess the Keynesian and Friedman views of speculation.    Speculative extremes are ranked by weight of activity and intensity of sentiment.  In either case, the extreme says little about the future, suggesting that speculation is more than just noise and that there is some informational content that is being passed through to the price. A unique dataset of risk-reversal skew on option prices is used to measure the weight of speculative sentiment.  This is supplemented with regulatory data on the weight of speculative positions.  
\end{abstract}

@@

This is a contrast between an idea of speculative activity as a nuisance that, at its most extreme, will likely to cause booms and reversals as bubbles expand and burst to discourage fundamental long-term investors from participating.  It is noise that does not emerge randomly, but feeds off itself as a feedback of sentiment  encourages  trends and serial correlation in asset price returns.  The alternative view regards speculation as an key lubricant of financial market as it provides liquidity and facilitates price discovery. In this view, speculation is stabilising and its absence will increase volatility and will undermine the process of price discovery.

The aim of this paper is to understand more about the nature of speculation by focusing on the foreign exchange market, using this to assess the relationship between the intensity or the weight of speculation and the movement of prices.  If speculators are uninformed and their activity can be regarded as noise, their most extreme sentiment and the time when speculators have the greatest weight in market activity should be those when price reversals are most likely to take place.  A unique set of option prices are used to measure the intensity of speculative sentiment.  US regulatory positions measure the prominence of speculators in the market. If speculation is stabilising, the largest weight of positions should be associated with stability and extremes of sentiment will drive prices towards equilibrium; if specualtion is destabilising, the largest positions should increase volatilit and extemes of sentiment would increase the risk of violent reversal back towards equilibrium.
